Aa Language Reference Manual

### 2020-07-26 v2/Ahir-asm/devel/docs/AaLRM.tex

>>>>

\subsection{Reporting and trace statements}

It is possible to convert an {\bf Aa} description
to C and then execute this C description.  During
the execution, we can generate log messages using the
following statement:
\begin{verbatim}
$rreport (Descriptor  Comment  var1 var2 .. varn)
\end{verbatim}
This generates a message during execution with
the following format.
\begin{verbatim}
Descriptor    Comment
         var1 <var1-value>
         var2 <var1-value>
         ....
         varn <varn-value>
\end{verbatim}

Another useful statement is the assert statement.
\begin{verbatim}
$assert (expr)
   $rreport (Descriptor  Comment  var1 var2 .. varn)
\end{verbatim}
This prints a report if expr is false, and then
exits the execution.

Finally, we have
\begin{verbatim}
$trace simple-identifier [ ( integer-level) ]
\end{verbatim}
This produces a message
\begin{verbatim}
TRACE simple-identifier
\end{verbatim}
it the trace-level (set in the execution of the AA2C
model) is set to integer-level or lower.

Note that these statements are not converted to hardware.
